Reanalysis Step 4: Propensity Score Analysis with Twang

### 2025-08-31 reanalysis-4-propensity_scores.qmd
n cores bug

# Set up parallel processing
# Reduce cores for memory-intensive GBM models
available_cores <- detectCores()
# Use fewer cores to avoid memory issues - each GBM model needs substantial memory
n_cores <- min(max_cores_for_ps, available_cores - 1)  # Use configured max cores to ensure sufficient memory per worker
log_message(paste0("Parallel processing: Using ", n_cores, " cores (of ", available_cores, " available) to manage memory usage"))

@@

# Create node tracking
node_counter <- 0
get_next_node_id <- function() {
  node_counter <<- node_counter + 1
  return(node_counter)
}

# Create assignments of imputations to node IDs
imputation_node_assignments <- data.frame(
  imputation = 1:n_imputations,
  node_id = NA
)

# Assign node IDs based on batch processing
batch_size <- ceiling(n_imputations / ceiling(n_imputations / n_cores))
for (i in 1:n_imputations) {
  imputation_node_assignments$node_id[i] <- get_next_node_id()
}

>>>>

# Set up parallel processing
# Reduce cores for memory-intensive GBM models
available_cores <- detectCores()
# Use fewer cores to avoid memory issues - each GBM model needs substantial memory
# Don't subtract 1 from max_cores_for_ps since it's already the desired limit
n_cores <- if (available_cores > max_cores_for_ps) max_cores_for_ps else max(1, available_cores - 1)
log_message(paste0("Parallel processing: Using ", n_cores, " cores (of ", available_cores, " available) to manage memory usage"))

@@

# Create assignments of imputations to node IDs
# Each imputation gets a unique sequential ID for tracking
imputation_node_assignments <- data.frame(
  imputation = 1:n_imputations,
  node_id = 1:n_imputations  # Simple sequential numbering: 1, 2, 3, 4, etc.
)
